Defining properties regulating pioneer-factor binding and function

### 2023-02-09 manuscript/manuscript_sections/_05_Methods.qmd
add CUT&RUN analysis to methods

@@

Raw ATAC-seq reads were trimmed to remove adapter sequences using NGmerge version 0.3 [@Gaspar2018].
Trimmed reads were aligned to the *Drosophila melanogaster* genome (version dm6) using bowtie2 with paramters -k 2 \--very-sensitive \--no-mixed \--no-discordant -X 5000.
Reads with a mapping quality \< 30 and reads aligning to the mitochondrial genome or scaffolds were discarded.
As described previously, only fragments \< 100bp were considered for downstream analysis [@Buenrostro2013].
Reads were combined across all replicates and peak calling was performed using MACS2 with parameters -f BAMPE \--keep-dup all -g dm \--call-summits.
featureCounts was used to count the number of reads aligning within 200bp (100bp upstream or downstream) of peak summits.
Differential accessibility analysis was performed using DESeq2.
Regions with an adjusted p-value \< 0.05 were considered differentially accessible.

@@

Trimming

Alignment

Filtering

peak calling

bigwigs

z-score normalization

spike-in normalization

>>>>

---
editor: 
  markdown: 
    wrap: sentence
---

@@

Raw ATAC-seq reads were trimmed to remove adapter sequences using NGmerge version 0.3 [@Gaspar2018].
Trimmed reads were aligned to the *Drosophila melanogaster* genome (version dm6) using bowtie2 with paramters -k 2 \--very-sensitive \--no-mixed \--no-discordant -X 5000.
Reads with a mapping quality \< 30 and reads aligning to the mitochondrial genome or scaffolds were discarded.
As described previously, only fragments \< 100bp were considered for downstream analysis [@Buenrostro2013].
Reads were combined across all replicates and peak calling was performed using MACS2 with parameters -f BAMPE \--keep-dup all -g dm \--call-summits.
featureCounts was used to count the number of reads aligning within 200bp (100bp upstream or downstream) of peak summits.
Generation of z-score normalized bigWig files was performed as described above for ChIP-seq data.
Differential accessibility analysis was performed using DESeq2.
Regions with an adjusted p-value \< 0.05 were considered differentially accessible.

@@

Trimming, alignment, and quality filtering of CUT&RUN reads was performed as described above for ATAC-seq data.
Peak calling was performed using MACS2 with parameters --broad -f BAMPE --keep-dup all -g dm.
Generation of z-score normalized bigWig files was performed as described above for ChIP-seq data.
The percentage of reads containing barcoded Epicypher nucleosomes was calculated and 1 divided by this percentage was used as the scaling factor for spike-in normalization.
The z-score normalized read depth was multiplied by these scaling factors to generate spike-in normalized bigWigs.
